---
title: 'UCLA ECON 441A: Applied Data Management'
author: ""
date: "10/22/2020"
output:
  pdf_document: default
  html_document: default
subtitle: Homework 1
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## (0) Clean console and call packages	
	
```{r}
#rm(list=ls(all=TRUE))
#cat("\014")	    #Cleans console

#install.packages('siebanxicor')
#install.packages('jsonlite')
#install.packages('GET')
library(siebanxicor)
library(jsonlite)
library(httr)
library(ggplot2)

```


## (1) Banxico's API Wrapper

We can get the API key from the Central Bank of Mexico in the following link:

https://www.banxico.org.mx/SieAPIRest/service/v1/token

The easy way is using "siebanxicor" library. 

The first step is to create the API key on the central bank's website. Once we 
generated it, we type the next command and the API key:

```{r}

setToken("bafc26d5c3c13e17b465d9550a5f38ca5f888a4dc8c6661ef3658720ba1702a9")

```

The second step is to retrieve the series id from its webpage. Then, we plug the id's
in the next function as show below:

```{r}

idSeries <- c("SF43718","SF46410","SF46407") #id's series
series <- getSeriesData(idSeries, '2000-01-01','2018-07-12') #We establish the initial and final date
serie <- getSerieDataFrame(series, "SF43718") #we convert the data into dataframe

```

This way is convenient because we can plot easily the time series using "ggplot2"

```{r}
ggplot(NULL, aes(x=date, y=value)) +
  geom_line(color="#ff1a1a", data = getSerieDataFrame(series, "SF43718")) +
  geom_line(color="#0000b3", data = getSerieDataFrame(series, "SF46410")) +
  geom_line(color="#00b300", data = getSerieDataFrame(series, "SF46407"))

```

## (2) Banxico's API 

We use the packages "jsonlite" and "httr" to generate the database by ourselves in JSON format.

Note that Banxico's API has a consult limit that only allows consulting up to 20 series. 
The series id catalog is in the next link:

https://www.banxico.org.mx/SieAPIRest/service/v1/doc/catalogoSeries

Once we know the series to consult and get the API key, we proceed to set the parameters.

```{r}
API_key_banxico <- "bafc26d5c3c13e17b465d9550a5f38ca5f888a4dc8c6661ef3658720ba1702a9"
initial_date <-"2010-01-01"
final_date <-"2020-07-01"
series_id_banxico <- "SF1,SR16734,SF331450,SE27803,SF17908"

```

The following part creates the function that will allow us to download data from Banco de Mexico economics database.

```{r}
banxico_get_series <- function(API_key_banxico, series_id_banxico, initial_date, final_date){
  URL <- "https://www.banxico.org.mx/SieAPIRest/service/v1/series/"
  parameters <- paste(series_id_banxico,"/datos/",initial_date,"/",final_date,"?token=",API_key_banxico,sep ="")
  PATH <- paste0(URL, parameters)
  query_banxico <- fromJSON(PATH)
return(query_banxico$bmx$series)
}

```

Once we created the function, we proceed to store the time series as shown below:

```{r}

data_banxico <- banxico_get_series(API_key_banxico, series_id_banxico, initial_date, final_date)

```

However, we face a problem which consists that the observations are stored in list format, which 
is inconvenient for our purposes. We need to extract that data and convert it into dataframe. 

```{r}

k <- 127
n <- length(data_banxico$datos)

mtx_banxico <- matrix(NA,k,n)

for (i in 1:n){
  mtx_banxico[,i] <- as.numeric(gsub(",","",data_banxico$datos[[i]][,2]))
}

mtx_banxico <- as.data.frame(mtx_banxico)
colnames(mtx_banxico) <- c(data_banxico$titulo[1],
                           data_banxico$titulo[2],
                           data_banxico$titulo[3],
                           data_banxico$titulo[4],
                           data_banxico$titulo[5])

```

Once we set the data ready, we print it on R and then export it in csv format.

```{r}
print(tail(mtx_banxico))
```

And we export it as follows:

```{r}

write.csv(mtx_banxico,"Banxico_database.csv", row.names = TRUE)

```


## (3) National Institute of Statistics and Geography of Mexico's API

We generate our own API key in the following link:

https://www.inegi.org.mx/servicios/api_indicadores.html

And we repeat the proccedure by setting the parameters:

```{r}
API_key_inegi <- "36c55a30-5b09-f211-164e-06da067a41af"
series_id_inegi <- c("444609","444568")

```

The next step is to create the function of INEGI's API.

```{r}
inegi_get_series <- function(API_key_inegi, series_id_inegi){
  mtx_inegi <- matrix(NA,0,length(series_id_inegi))
  URL <- "https://www.inegi.org.mx/app/api/indicadores/desarrolladores/jsonxml/INDICATOR/"
  for (i in series_id_inegi){
    parameters <- paste(i,"/es/0700/false/BIE/2.0/",API_key_inegi,"?type=jsonp",sep ="")
    PATH <- paste0(URL, parameters)
    query_inegi <- fromJSON(PATH)
    mtx_inegi[i] <- query_inegi$Series$OBSERVATIONS[[1]][2]
  }
  return(mtx_inegi)
  
}

```

We run our function:

```{r}

data_inegi <- inegi_get_series(API_key_inegi,series_id_inegi)

```

Then we convert our data from list format to matrix format.

```{r}
mtx_inegi <- matrix(NA,183,2)

for (i in 1:2){
  mtx_inegi[,i] <- as.numeric(gsub(",","",data_inegi[[i]]))
}

colnames(mtx_inegi) <- c("Informal Employment Rate","Self-Employed Workers")

```

An finally we check that we did correctly the process by printing the last part of 
the database and then we export it in csv format.

```{r}
print(tail(mtx_inegi))

write.csv(mtx_inegi,"INEGI_database.csv", row.names = TRUE)

```

## (4) Twitter's API Mocker

In this section we show the code to get the Twitter's credentials in order to use their data.
However, we only show some basics such as monetary base (base monetaria in Spanish), and other 
key words related to cash demand.

```{r}
#install.packages("rtweet")
library(rtweet)
an <- "base_mon"
ak <- "e1FYKkEzVeg6TYtP7Ta4etfTC"
ask <- "l8Uw6fDdMdxSOXzEsGNQXreSLNBsyKAb2jeXaNGUKYqgNPjE4V"
at <-"558587999-zwP08BA5Mq2UVlJZ58pUEfRgKUmZlIWUJXnym6mq"
ats<- "MCLClo4NyXjK9GstJuZRnX2Tidn1yGKasjxakbFFdQ5YT"
create_token(an,ak,ask,at,ats) #create token
```

Once we created the token, we can plot some words tweeted in recent days.

```{r}

#monetary_base <- search_tweets(q = "base monetaria", n=5000,lang="es", include_rts = FALSE)
#ts_plot(monetary_base)

```


However, we faced problems when we tried to knit r markdown, so we could not
show the graph on this pdf.


## (5) Comments on the Data

This homework will help us in the future to run our econometric model of money demand for Mexico. 
The purpose of creating the API of Banco de Mexico and INEGI is that those institutions publish 
the macroeconomic data  of Mexico. In particular, for the Banco de Mexico's case we created a 
function to download the data of the Monetary Base, the monetary policy interest rate, the 
monthly indicator of production, and the remittances. On the other hand, the INEGI's API will 
help us to collect the data of the informal sector occupation rate and self-employed workers, 
since these indicators are useful to explain the money demand in Mexico. 

For the Twitter's API there is more work to do in order to build a variable that will try to measure 
the daily seasonality of the money demand in Mexico by searching for key words in Mexico,
such as "money", "cash machines", "payments", "withdrawals", "holidays", or any 
other words that would be useful to include in our model. 

