---
title: "Econ 441A API Homework"
author: ""
date: "10/21/2020"
output: pdf_document
---

```{r, echo=FALSE, warning=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, echo=FALSE, warning=FALSE, message=FALSE}
#Import Package
library(jsonlite)
```

##############
# I. Asteroid Close Encounter Dataset
##############
This dataset includes the asteroids that came within 0.001 astronomical units of earth in the past year and the dates of these occurrences.  
It can be used to check how often our planet has close encounters with asteroids.

```{r, warning=FALSE, message=FALSE}
#Create a variable for the URL for NASA close encounters.
NASAURL = paste("https://ssd-api.jpl.nasa.gov/cad.api")

#Specify data for just asteroids that came very close (within 0.001 astronomical units) to earth in the past year.
NASAparameters = "?kind=a&date-min=2019-10-21&date-max=2020-10-21&dist-max=0.001"

#Generate path with url and parameters.
NASAPath = paste(NASAURL, NASAparameters, sep = "")

#Get info about asteroids that came close to earth in the past year.
NASAquery = jsonlite::fromJSON(NASAPath)
NASAdata = NASAquery$data
NASAdata
```
```{r, warning=FALSE, message=FALSE}
#Now create a dataframe of the asteroids' names and the dates we had close encounters with them.
names = NASAdata[,1]

dates = NASAdata[,4]

Dataset1 = data.frame (
  Asteroid = names,
  Date = dates
)

#Change the format of the dates & times to YYYY-MM-DD.
Dataset1$Date = substr(Dataset1$Date,1,11)
Dataset1$Date = as.Date(Dataset1$Date, format = "%Y-%b-%d")

Dataset1

#Export the dataset to a csv.
write.csv(Dataset1,"Asteroids.csv", row.names = TRUE)
```

##############
# II. Covid-19 Cases and Deaths by Country Dataset
##############
This dataset includes the total number of Covid-19 cases and deaths experiences by every world nation.   
It can be used to check which countries have been the most affected by the pandemic.

```{r, warning=FALSE, message=FALSE}
#Call data from the worldwide Covid-19 case API.
CovidURL = paste("https://api.covid19api.com/summary")
Covidquery = jsonlite::fromJSON(CovidURL)

Covidquery
```

```{r, warning=FALSE, message=FALSE}
#Create a dataframe of countries, their total cases and deaths using the Covid-19 API data.
Dataset2 = data.frame (
  Country = Covidquery$Countries$Country,
  Confirmed_Cases = Covidquery$Countries$TotalConfirmed,
  Total_Deaths = Covidquery$Countries$TotalDeaths
)

Dataset2

#Export the dataset to a csv.
write.csv(Dataset2,"CovidCases.csv", row.names = TRUE)
```
