---
title: ""
author: ""
date: "2020/10/21"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

1. This dataset contains the total amount of crime in California by year from 1979 and the unemployment rate in CA during the same period. It could be used to measure to what extent dose the unemployment rate influence the crime rate in California.
```{r}
#for crime data
apikey_cde="wMOccIpuR9akoqRv3Gmgqhf0PO7vd44kOSat1Bfj"
from=1979
to=2019
stat_abbr="CA"
CDE_crime=function(apikey,from,to,stat_abbr){
  URL="https://api.usa.gov/crime/fbi/sapi/api/arson/states"
  PATH=paste0(URL,"/",stat_abbr,"/",from,"/",to,"?API_KEY=",apikey)
  initialqury=jsonlite::fromJSON(PATH)
  df=initialqury$results
  df=df[c("reported")]
  return(df)
}
#for unemployment rate:
apikey_fred="54b39d1f56f337fef917b0b1592874cc"
series_id="CAUR"
observation_start="1979-01-01"
observation_end="2019-01-01"
frequency="a"
fred_series=function(APIkey,series_id,observation_start,
                     observation_end,frequency){
  URL="https://api.stlouisfed.org/fred/series/observations"
  parameters=paste0(
    "?series_id=",series_id,
    "&api_key=",APIkey,
    "&observation_start=",observation_start, 
    "&observation_end=",observation_end,
    "&frequency=",frequency,
    "&file_type=json"
  )
  PATH=paste0(URL,parameters)
  initialqury=jsonlite::fromJSON(PATH)
  df=initialqury$observations
  df=df[c("value")]
  df$value=as.numeric(df$value)
  return(df)
}
crime=CDE_crime(apikey_cde,from,to,stat_abbr)
unem=fred_series(apikey_fred,series_id,observation_start,
                     observation_end,frequency)
years=1979:2019
dataset1=cbind(years,crime,unem)
colnames(dataset1)=c("year","crime","unemployment_rate")
write.table(dataset1,file="Dataset1.csv",sep = ",",row.names=FALSE)
```

2. This dataset contains manufactures and service exports of United Kingdom to the wolrd from 2005 to 2018. It can be used to intuitively estimate the impact of Brexit on UK's export and its trend through time.
```{r}
headers = c('Ocp-Apim-Subscription-Key' = "e14bb852a6214d7e8862b7f255b70c14") 
i1='ITS_MTV_AX'
pc1='MA'
i2='ITS_CS_AX6'
pc2='S'
wto_data=function(i,pc){
  params = list()
  params['i'] = i
  params['r'] = '826'
  params['p'] = '000'
  params['ps'] = '2005-2018'
  params['pc'] = pc
  params['spc'] = 'false'
  params['fmt'] = 'json'
  params['mode'] = 'full'
  params['dec'] = 'default'
  params['off'] = '0'
  params['max'] = '500'
  params['head'] = 'H'
  params['lang'] = '1'
  params['meta'] = 'false'
  
  PATH = paste0("https://api.wto.org/timeseries/v1/data?"
                     , paste0(names(params),'=',params,collapse = "&")) 
  resp <- httr::GET(PATH,
                     add_headers(headers)) 
  
  if(!http_error(resp)){ #Checks for an http error
    jsonRespText<-jsonlite::fromJSON(rawToChar(content(resp,encoding = 'UTF-8')))$Dataset # Converts the UTF-8 file into JSON
    jsonRespText
  }else{
    stop('Error in Response')
  }
  ord_json=jsonRespText[order(jsonRespText$Year),]
  df=ord_json[c("Value")]
  return(df)
}
goods_ex=wto_data(i1,pc1)
serv_ex=wto_data(i2,pc2)
year=2005:2018
Dataset2=cbind(year,goods_ex,serv_ex)
colnames(Dataset2)=c("years","good_ex","serv_ex")
write.table(Dataset2,file="Dataset2.csv",sep = ",",row.names=FALSE)
```

