---
title: "Two Datasets from API's"
author: ""
fontfamily: mathpazo
output:
  pdf_document:
    toc: yes
  fig_caption: yes
  highlight: haddock
  number_sections: yes
  df_print: paged
  html_document:
    toc: yes
    df_print: paged
fontsize: 10.5pt
editor_options: null
chunk_output_type: console
--- 
```{r, echo=FALSE, warning=FALSE, message= FALSE}
library(knitr)
opts_chunk$set(tidy.opts=list(width.cutoff=100))
```

```{r, echo=FALSE, warning=FALSE, message= FALSE}
#Import Package
library(jsonlite)
```

# API Dataset 1
```{r}
product_type = "eyeliner"
product_category = "liquid"
price_less_than = 8
rating_greater_than = 3

URL = paste("http://makeup-api.herokuapp.com/api/v1/products.json?", "product_type=", product_type, "&", "product_category=", product_category, "&", "price_less_than=", price_less_than, "&", "rating_greater_than=", rating_greater_than, sep = "")
PATH = paste(URL, sep = "")

initialquery = jsonlite::fromJSON(PATH)

print(initialquery)

df_liner = data.frame(initialquery)
df_liner = as.matrix(df_liner)

write.csv(df_liner, "/Users/madelyncaufield/Desktop/ECON441A Applied Data Management for Economists\\MyMakeupbrandData.csv", row.names = FALSE)
```
This dataset contains the price of different liquid eyeliners and their associated ratings. The data could be used to measure the liquid eyeliner that gives you the most bang for your buck at the highest rating. We could change parameters accordingly to either meet a certain price or rating threshold depending on the consumers budget and preference. 

# API Dataset 2
```{r}
output <- data.frame(matrix(ncol = 2, nrow = 0))
colnames(output) <- c("Date", "Articles")

get_num_articles <- function(month, year, words, APIkey){
  URL = paste("https://api.nytimes.com/svc/archive/v1/", year, "/", month,".json?", sep = "")
  PATH = paste(URL, "api-key=", APIkey, sep="")
  initialquery = jsonlite::fromJSON(PATH)
  
  df = as.data.frame(initialquery$response$docs)
  
  booleans = grepl(words, df$abstract, fixed=TRUE)
  mentions = sum(booleans)
  
  temp <- data.frame(Date = paste(year , "/" , month, sep = ""), Articles =  mentions)
  return(temp)
}

words ="Democrat"
APIkey = "Rooe4zcigoDA1qD1HHlNs3FvqpyMUL1x"

months = c(1:10) 
years = c(2020)
for(year in years){
  year = toString(year)
  for (month in months){
    month = toString(month)
    temp = get_num_articles(month,year, words, APIkey)
    output = rbind(output,temp)
  }
}
  
output

write.csv(output, file = 'exported_Democrat_data.csv')
```

```{r}
output2 <- data.frame(matrix(ncol = 2, nrow = 0))
colnames(output2) <- c("Date", "Articles")

get_num_articles <- function(month, year, words, APIkey){
  URL = paste("https://api.nytimes.com/svc/archive/v1/", year, "/", month,".json?", sep = "")
  PATH = paste(URL, "api-key=", APIkey, sep="")
  initialquery = jsonlite::fromJSON(PATH)
  
  df = as.data.frame(initialquery$response$docs)
  
  booleans = grepl(words, df$abstract, fixed=TRUE)
  mentions = sum(booleans)
  
  temp <- data.frame(Date = paste(year , "/" , month, sep = ""), Articles =  mentions)
  return(temp)
}

words ="Republican"
APIkey = "Rooe4zcigoDA1qD1HHlNs3FvqpyMUL1x"

months = c(1:10) 
years = c(2020)
for(year in years){
  year = toString(year)
  for (month in months){
    month = toString(month)
    temp = get_num_articles(month,year, words, APIkey)
    output2 = rbind(output2,temp)
  }
}
  
output2

write.csv(output2, file = 'exported_Republican_data.csv')
```
The dataset contains the number of articles that mention the word "Democrat" and/or "Republican" in the abstract from 01/2020 up until this month, 10/2020. The data could be used to measure recent political bias in the New York Times media surrounding this years election, however the data does not account for opinionated versus objective articles. 

THE END. 
