---
title: "441Homework"
author: "Tanaporn Sriklay"
date: "10/25/2020"
output: pdf_document
---

```{r, echo=FALSE, warning=FALSE, message= FALSE}
library(knitr)
opts_chunk$set(tidy.opts=list(width.cutoff=70))
```

## Load library

```{r libraries, echo=FALSE, warning=FALSE, message=FALSE}
library(jsonlite)
library(openxlsx)
library(dplyr)
library(openxlsx)
library(OECD)
```

##API Data set 1 
Source: https://openchargemap.org

This data set is the information of battery charging station in many countries.
The country with the most electric vehicles are used in the example of coding, 
including China, USA, Japan and UK.

The data includes the general information of the provider of charging services 
such as the address, the charging level (suggesting the charging time), and 
the usage cost and the requirement for services (i.e. membership, public use,
private use)

Also, the data includes the information of the customer side such as the type
of charging (i.e. power, voltage ), capability of fast-charging, connection type,
status of charging (i.e. fail to charging? because?) and comments.

#The possible questions by using the data:

1. How much difference in charging infrastructure in each country? (i.e. in term
of price, type of providers, type and quality of charging)

2. Do those difference lead to the varying proportion of electric cars use 
among countries?

3. What is the determinants of location of the charging station ?

#Here is the coding for loading API Data 
```{r, warning=FALSE, message=FALSE}
APIkey = "e67121f20c15f2fa5dc000b94fb6bdb0"

#selected country
series_id = c("US", "CN","GB", "JP")

#function to create link API
battery_series <- function(APIkey, country_id, max){
  URL = "https://api.openchargemap.io/v3/poi/?output=json"
  parameters = paste(
  paste0("countrycode=", country_id), #define the seried_id
  paste0("maxresults=",max),sep="&")#maxresults= maximum of data in each countries 
  link = paste(URL,parameters, sep = "&")
}
#creating API path 
PATH <- battery_series(APIkey,series_id, 100) 
#Loading the API data
datalist = list()
for (i in series_id) {
  n = n + 1
  data = fromJSON(battery_series(APIkey,i, 100)) #Transform the JSON file
  data1 = as.data.frame(data) 
  datalist[[n]] = data1 #colect each element of data in list
}
#append data in the list by rows
big_data <- bind_rows(datalist)
```

#Here is the coding for selecting the interesting variables and transformed them
#in to dataframe

```{r, warning=FALSE, message=FALSE}
#Data about service provider
c1 = big_data$OperatorInfo$Title #Title of provider
#Data about the requirement of usage
c2 = NULL
for(i in 1: length(big_data$UsageType)) {
  c2 <- cbind(c2, unlist(big_data$UsageType[i])) #aggregate element
}
colnames(c2) <- as.vector(names(big_data$UsageType))#change column name
rownames(c2) <- c() #delete row name
#Date of data
c3 <- big_data$DateLastVerified
#Price rate
c4 <- big_data$UsageCost
#Address of Provider
c5_1 <- big_data$AddressInfo[,c(2,3,5,6,7,8,10,11)] # select title and address
c5_2 <- big_data$AddressInfo$Country$ISOCode # select country name
c5 <- cbind(c5_1,c5_2)

#Data on customer side
c6 = NULL

  contype = list()
  ID = list()
  status = list()
  leveID = list()
  comment = list()
  commenttitle = list()
  isfast = list()
  amp = list()
  vol = list()
  power = list()
  quan = list()
  comment2 =  list()
for (i in 1:length(big_data$Connections)){
  ID[[i]] = big_data$Connections[[i]]$ID
  contype[[i]] = big_data$Connections[[i]]$ConnectionType$Title
  status[[i]] = big_data$Connections[[i]]$StatusTypeID
  leveID[[i]] = big_data$Connections[[i]]$LevelID
  commenttitle[[i]] = big_data$Connections[[i]]$Level$Title
  isfast[[i]] = big_data$Connections[[i]]$Level$IsFastChargeCapable
  amp[[i]] = big_data$Connections[[i]]$Amps
  vol[[i]] = big_data$Connections[[i]]$Voltage
  power[[i]] = big_data$Connections[[i]]$PowerKW
  quan[[i]] = big_data$Connections[[i]]$Quantity
  comment2[[i]] =  big_data$Connections[[i]]$Comments
}
ID = unlist(ID)
contype = unlist(contype)
status = unlist(status)
leveID = unlist(leveID)
commenttitle = unlist(commenttitle)
isfast = unlist(isfast)
amp = unlist(amp)
vol = unlist(vol)
power = unlist(power)
quan = unlist(quan)
comment2 = unlist(comment2)
c6 <- cbind(ID,contype, status, leveID,commenttitle,isfast,amp,vol,power,quan,comment2)
rownames(c6) = c()
#GeneralComments
c7 = big_data$GeneralComments
#aggregate data about provider
totalv = cbind(c1,c2,c3,c4,c5,c7)
#change name of colum
names(totalv)[1] = "Provider"
names(totalv)[7] = "Dataver"
names(totalv)[8] = "Usagecost"
names(totalv)[17] = "country" 
names(totalv)[18] = "Generalcomment"
#change c6 to data frame
c6frame= data.frame(c6)
c6frame %>% distinct(ID, .keep_all = TRUE)

```

##API Data set 2
From OECD API wrappers

OECD provide a lot of data. In this coding, I use API wrappers to get the data 
of the original value added of exports by each regions. I plan to use this data
in my project to answer what's determine the trade pattern and GVCs in the
future. This value will be used to measure size of supply chains in each regions
by industry. Also, I use Api to get the data about trade in service because
I believe the future supply chain are developed together with services. 


```{r, warning=FALSE, message=FALSE}
#list of database
dataset_list <- get_datasets()
#search data set of interesting variable i.e. orign of value added in gross export
search_dataset("Value Added", data = dataset_list)
search_dataset("service", data = dataset_list)
#Define our interested data
dataset = "TIVA_2018_C2"
dataset2 = "TISP"
#Get the structure of data
dstruc <- get_data_structure(dataset)
str(dstruc, max.level = 1)
#Showing the variable & dimensions
dstruc$VAR_DESC
#i.e. want to know the country code of exporting country
dstruc$XCTRY
#Filter the targeted country, 
filter_list = list(c("WLD", "ASEAN", "EASIA", "EU15","EU28","ZNAM","ZSCA","G20"))
#Get data given filter
datav <- get_dataset(dataset = dataset, filter = filter_list)
datas <- get_dataset(dataset = dataset2)
```


#Here is the code for exporting Excel 
```{r, warning=FALSE, message=FALSE}
createSpreadsheets <- function(name,r1,r2,r3,r4){
  ## Create new workbooks
  wb <- createWorkbook() 
  
  ## Create the worksheets
  addWorksheet(wb, sheetName = "set1_Producer" )
  addWorksheet(wb, sheetName = "set1_Consumer" )
  addWorksheet(wb, sheetName = "set2_originofva" )
  addWorksheet(wb, sheetName = "set2_tradeservice" )
  ## Write the data
  writeData(wb, "set1_Producer", r1)
  writeData(wb, "set1_Consumer", r2)
  writeData(wb, "set2_originofva", r3)
  writeData(wb, "set2_tradeservice", r4)
  
  ## Save workbook to working directory 
  saveWorkbook(wb, file = paste(name,".xlsx", sep=""), overwrite = TRUE)
}

## create spreadsheets b
  createSpreadsheets("441homework",totalv,c6frame,datav,datas)
```  
