---
title: "441a HW1"
author: ""
date: "10/22/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
getwd()
library(jsonlite)
```

# 1. Dataset 1
This dataset gives us the real median household income in the United States and allows us to 
see how it has progressed over time.
Question: How much has median household income grown in the past century?
```{r}
APIkey = "318785ae75448b5f1b3788a9690b3417"
series_id = "MEHOINUSA672N"
realtime_start = "1980-01-01"

URL = "https://api.stlouisfed.org/fred/series/observations"

parameters = paste("?series_id=", series_id, 
"&realtime_start=",realtime_start,
"&api_key=",APIkey,
"&file_type=json",
sep="")
PATH = paste0(URL, parameters)
#PATH
query = jsonlite::fromJSON(PATH)
MedHIncome = query$observations
#rownames(MedHIncome) <- MedHIncome$date

MedHIncome = MedHIncome[c("date", "value")]
MedHIncome$value <- as.numeric(MedHIncome$value)

write.csv(MedHIncome,"C:/Users/Carlos Hernandez/Documents/R\\MedHouseIncome.csv", row.names = TRUE)
```






# Dataset 2:
This Data comes from sportsdata.io and details stats where we can analyze player stats during the 2016 season.
The roundid indicates a specific league/ competition. Initialquerys is my dataset and at the end I narrow the data
to see the number of minutes each player plays.

Question: The correlation between minutes played and fantasy points? What effect does goals scored have on this?

https://api.sportsdata.io/v3/soccer/stats/json/PlayerSeasonStats/1?key=ae98d45adaff42378acf9496227c1158
```{r}
APIkey = "ae98d45adaff42378acf9496227c1158"
roundid = 7

URL = "https://api.sportsdata.io/v3/soccer/stats/json/PlayerSeasonStats/"

parameters = paste(roundid, "?key=", APIkey,
sep="")

PATH = paste0(URL, parameters)
#PATH
initialquerys = jsonlite::fromJSON(PATH)

df = initialquerys
df_focus = df[c("Name", "Team","Minutes","FantasyPoints", "Goals", "Shots")]
#df_focus



write.csv(df_focus,"C:/Users/Carlos Hernandez/Documents/R\\SoccerAPIrDataset.csv", row.names = TRUE)
```

# Dataset 3:
This data from alphavantage.co shows a time series of monthly changes in currency exchange 
and can provide us with an understanding of changes in the currencies we select.
Potential Question: In what direction is the currency exchange of Euro and USD heading?

**I did not finish this

https://www.alphavantage.co/query?function=FX_MONTHLY&from_symbol=EUR&to_symbol=USD&apikey=demo
```{r}
APIkey = "41D7AWDTZ15E3Q78"
Function = "FX_MONTHLY"
from_symbol = "EUR"
to_symbol = "USD"
size = "compact" #shows last 100 data points for equity. the other option is "full"

URL2 = "https://www.alphavantage.co/query?"

parameters2 = paste("function=", Function,
  "&from_symbol=",from_symbol,
  "&to_symbol=", to_symbol,
  "&outputsize=", size,
  "&apikey=", APIkey,
  sep="")

PATH2 = paste0(URL2, parameters2)
#PATH2
initialquery2 = jsonlite::fromJSON(PATH2)
TimeSMonthly = initialquery2$`Time Series FX (Monthly)`
#as.data.frame(TimeSMonthly)
```


