---
title: "Data Management API HW"
author: ""
date: "10/23/2020"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
#Import Package
library(jsonlite)
library(tidyverse)
library(data.table)
```

# Homework 1

## Write function to pull first dataset from the API

```{r}
cdeArrest = function(offense, variable, start, end, 
                     api_key = "9rfkv4GTRHYsXXOaZq8UYM1YJeW2Y3P9C0NrCSdt"){
  URL = paste("https://api.usa.gov/crime/fbi/sapi/api/data/arrest/national/")
  PATH = paste(URL, offense , "/", variable, "/", start, "/", end, 
               "?API_KEY=", api_key, sep = "")
  initialquery = jsonlite::fromJSON(PATH)
  rawfm = initialquery$results
  return(rawfm)
}

#Female/male arrest data
fmFraud = cdeArrest("fraud", "monthly", "1985", "2017")
fmFraud = fmFraud %>%
    select(data_year, male_count, female_count) %>%
    mutate(proportion_female = female_count/sum(male_count,female_count))

# Race fraud arrest data
rfraud = cdeArrest("fraud", "race", "1985", "2017")
rfraud = rfraud %>%
    select(-csv_header)

#Buold joint DF
fraud_frame = left_join(fmFraud, rfraud)
```

This data set details the number total number of arrests for fraud by sex and race from 1985 to 2017. We could use this data to answer how the proportion of females arrested for fraud has changed over time. We can compute proportions for the other included demographics and make similar comparisons over time.

## Creating the second data set

The next data set takes advantage of the alpha vantage api, and the function below
retrieves data on apple stock over the last 100 days. I also pull data on SPY. 
```{r}
dailystock = function(ticker, output, apikey = "K7S5149DVD5I7SQ0"){
  URL = paste("https://www.alphavantage.co/query?function=TIME_SERIES_DAILY&symbol=")
  PATH = paste(URL, ticker, "&apikey=", apikey,"&outputsize=", output, sep = "")
  initialquery = jsonlite::fromJSON(PATH)
  priceraw = initialquery$`Time Series (Daily)`
  x = rbindlist(priceraw, idcol = TRUE)
  newnames = c('id', 'open',"high", "low", "close", "volume")
    x = x %>%
    rename_at(vars(names(x)), ~newnames)
  return(x)
}


# Retrieve/clean SPY ETF data
sp500 = dailystock("SPY", "compact")
sp500 = sp500 %>%
  select(id, close)
sp500$close = as.numeric(sp500$close)

#Retrieve/clean Apple Stock Data, create spread variable
applestock = dailystock("aapl", "compact")
applestock$close = as.numeric(applestock$close)
applestock$high = as.numeric(applestock$high)
applestock$low = as.numeric(applestock$low)

#Build a joint dataframe
apple500 = right_join(applestock, sp500, by = "id")

```

An example of a question this dataset could look at is how the the spread between 
high and low prices changes with trading volume. We could also look at the correlation between apple's stock price and the market (measured by SPY ETF movement).

## Export Data to csv
```{r}
write.csv(apple500, file = 'apple500.csv', row.names = FALSE)
write.csv(fraud_frame, file = 'fraud.csv', row.names = FALSE)
```

